MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-30 paper.Rmd
Adding README.txt file for IEA data.

```{r}
library(IEATools)
library(PFUSetup)
home_path <- "ExampleFolder"
iea_folder_path <- file.path(home_path, "IEA extended energy balance data")
iea_data_path <- file.path("IEA extended energy balance data", "GH-ZA-TJ-Extended-Energy-Balances-sample-2022.csv")
setup <- PFUSetup::get_abs_paths(home_path = file.path("ExampleFolder"), 
                                 dropbox_path = "",
                                 project_path = "",
                                 iea_folder_path = iea_folder_path,
                                 iea_data_path = iea_data_path,
                                 version = "v_example")
```

>>>>

```{r}
# Available on CRAN
# library(matsbyname)
# library(matsindf)
# library(RCLabels)

# Available from MatthewHeun on GitHub
# with devtools::install_github("MatthewHeun/xxxxxx")
# library(IEATools)

# Available from EnergyEconomyDecoupling on GitHub
# with devtools::install_github("EnergyEconomyDecoupling/xxxxxx")
# library(PFUPipelineTools)
library(PFUSetup)

# Use the PFUSetup package to establish paths for the example
home_path <- "ExampleFolder"
iea_folder_path <- file.path(home_path, "IEA extended energy balance data")
iea_data_path <- file.path("IEA extended energy balance data",
                           "GH-ZA-TJ-Extended-Energy-Balances-sample-2022.csv")
setup <- PFUSetup::get_abs_paths(home_path = file.path("ExampleFolder"), 
                                 dropbox_path = "",
                                 project_path = "",
                                 iea_folder_path = iea_folder_path,
                                 iea_data_path = iea_data_path,
                                 version = "v_example")
```
